### 2012-02-03 GUIErrorDetector/paper/evaluation.tex
improve introduction / abstract, and correct the wordings
changes based on new comments

Our experiment objective is three-fold: to demonstrate the effectiveness
of our approach in detecting real bugs in multithreaded GUI applications, to 
compare the reflection-aware call graph construction algorithm
with existing ones, and to evaluate the usefulness of the proposed 
 heuristics.

First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedure (Section~\ref{sec:procedural}).
We then show that our technique detects bugs in real-world GUI applications (Section~\ref{sec:errors}).
We also compare our technique with
a straightforward approach (Section~\ref{sec:straightforward}),  compare the reflection-aware call graph
construction algorithms with existing algorithms (Section~\ref{sec:reflectionaware}), and
evaluate different graph search strategies in error detection (Section~\ref{sec:search}).
 Finally, we show that the set of proposed heuristics are effective
in removing redundant warnings and eliminate false positives (Section~\ref{sec:filters}).

@@

We chose subjects belonging to various categories from all subjects satisfying
the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
which include end-user applications, programming tools, and games.

@@

\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox} implements a client that allows users
to drag and drop files, which are then uploaded to their Amazon S3 accounts. SodokuSolver~\cite{sudokusolver}
computes Sodoku solutions efficiently using mutlithreading execution.

@@

We ran our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without the reflection-aware algorithm 
(Section~\ref{sec:cg}).  We did not use other expensive algorithms like $k$-CFA ($k >$ 1),
because they can not scale to our subject programs.

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.35\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
\cline{2-12}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
\hline \hline
\multicolumn{12}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149 & 2 \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693 & 1 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202 & 1 \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 & 1 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210 & 1 \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356 & 2 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
 \hline
 Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 & 1 \\
\hline
\hline
 Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 & 11 \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding invalid thread access errors
in multithreaded GUI programs. Column ``CG Size'' shows the
call graph size in terms of node number. Column ``\#Warning''
shows the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Columns ``RTA '', ``0-CFA'',
and ``1-CFA'' show the results of using different
call graph construction algorithms. In each cell of the table
for Android applications, a slash ``/'' separates the result of
using normal call graph construction algorithm and the reflection-aware
call graph construction algorithm. The 6 errors found in VirgoFTP, FileBunker,
S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
results of a straightforward approach (Section~\ref{sec:straightforward}) are show at the far right.} }
\end{table*}

@@

Table~\ref{table:results} tabulates the results of running our
tool with three different call graph construction algorithms
on the subject programs. From these results, we can see our
tool found real errors from each subject on  four
supported GUI frameworks. The results vary slightly according
to the call graph algorithm used. In general, using
the 1-CFA algorithm found most errors (11 in total) and least
warnings (21 in total). The trade-offs of using other call graph
construction algorithms will be explained in Section~\ref{sec:reflectionaware}.

We further examined the detailed results for each subject.
Among the 21 warnings issued by using the 1-CFA algorithm, 11
warnings reveals 11 distinct errors, in which 6 are previously-unknown,
2 warnings are false positive, and the remaining 8 
are redundant warnings.

@@

As briefly mentioned in Section~\ref{sec:finding}, one way to prevent
invalid thread access errors is to wrap every GUI accessing operation
with message passing (i.e., via the safe methods). Thus, a
straightforward way to detect potential invalid error
is to check every method in the user code to determine whether all GUI-accessing operation
is probably wrapped. If not, this approach issues a warning.% for every violation. 
%If not, this approach issues warnings.

We implemented this straightforward approach and experimentally compared it
with our technique.% presented in Section~\ref{sec:technique}.
The far right column in Table~\ref{table:results} shows the results.
The results show that this straightforward approach can identify every
error that our technique has found, but issue a huge number of false
positives and redundant warnings. The primary reason is that this simple approach
does not globally reason about calling relationship between
threads, UI-accessing methods, and safe methods, thus it often incorrectly
classifies GUI accessing operations which will never be executed
in a non-UI thread as erroneous. Furthermore, our technique
outputs a method call chain with each reported error, which can help
developers understand how an invalid thread access error is triggered.

@@

We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors with less warnings than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph, and may
mix the same method calls by different callers into a single node, thus
introducing imprecision.

@@

In contrast, the error-related GUI objects in the other two Android applications (Fennec
and SGTPuzzler) are created explicitly, so that a normal call graph construction
algorithm can create a sufficiently complete call graph.

@@

The first variant uses DFS for graph traverse by changing method \CodeIn{getReachableStartsByBFS(cg)}
to \CodeIn{getReachableStartsByDFS(cg)} on line 7, changing line 9 to
$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
and changing queue operations (\CodeIn{enqueue} and \CodeIn{dequeue} on lines 11, 13, and 25 of Figure~\ref{fig:androiderror})
to the correspondiing statck operations (\CodeIn{push} and \CodeIn{pop}).

As a result, this variant found 8 errors in total and missed 1 error in the FileBunker subject.
The reason is that DFS tends to search deeper into the graph, and the path it returns
is more likely not to be the shortest one. In the FileBunker subject, the path
returned by DFS is much longer, and does not actually exist.

@@

The second variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from the start nodes, and then checks whether each
path spawns a new thread and accesses GUI object without using safe methods. As
a result, this variant run out of memory on all subjects. We checked
the output paths before the algorithm terminated, and found none of the explored
path revealed a valid error. This is because the number of
non-cyclic paths in a graph is exponentially large to the graph node number.
For a realistic call graph which often contains thousands of nodes, for which
it is impossible to enumerate all paths in practice.

@@

Table~\ref{table:filters} tabulates the results.
Our static analysis output thousands of warnings for the evaluated
subjects, but the proposed heuristic filters effectively reduced
the number of likely invalid warnings. On average, five heuristic
filters removed 99.96\% of the reported warnings as false positives
or redundant warnings. Specifically, heuristic filters 1 and 2 identified
32.48\% of the warnings as likely false positives, and filters 3, 4,
and 5 identified 67.48\% of the warnings as redundant warnings.
Remarkably, the 3rd heuristic filter for removing lexically redundant
reports is the most effective one on the evaluated subjects: it removes 35277 redundant warnings.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.81\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 Subject & Before & \#W & \#W & \#W & \#W& \#W \\
 Program & Filtering & $F_1$ & $F_2$ & $F_3$&$F_4$ & $F_5$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP &  21 &  21 &  3 & 3 &  2 & 2\\
 \hline
 FileBunker &  4494 &  3210 &  3210 &  642 &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1621 &  1487 &  1487 & 1487 &  6 & 6\\
 \hline
 HundsonEclipse&  3192 &  2417 &  1696 & 9 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  30975 & 9 &  1 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 2 &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  122 &  84 & 84 & 84 &  9 & 3\\
 \hline
 MyTracks &  1176 &  441 &  441 & 441 &  63 & 1 \\
\hline
 \hline
 Total &  56214 &  39708 &  37955 &  2678 &  89 & 21 \\
 \hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
heuristic filters (Section~\ref{sec:heuristic}). Column ``Before Filtering''
shows the output warning number using the reflection-aware 1-CFA algorithm.
Column ``\#W $F_i$'' represents the number of remaining warnings after applying
filters 1 -- $i$. Numbers in last column are taken
from Table~\ref{table:results}.
Results of using other algorithms show similar patterns, which are omitted for brevity.} }
\end{table}

>>>>

Our experiment objective is three-fold: to demonstrate the effectiveness
of our approach in detecting real errors in multithreaded GUI applications, to 
compare the reflection-aware call graph construction algorithm
with existing ones, and to evaluate the usefulness of the proposed 
 heuristics.

First, we describe our subject programs (Section~\ref{sec:subjects}) and the experimental procedure (Section~\ref{sec:procedural}).
We then show that our technique detects bugs in real-world GUI applications (Section~\ref{sec:errors}).
We also compare our technique with
a straightforward approach (Section~\ref{sec:straightforward}),  compare
different call graph construction algorithms (Section~\ref{sec:reflectionaware}), and
evaluate various graph search strategies in error detection (Section~\ref{sec:search}).
 Finally, we show that the set of proposed heuristics are effective
in removing redundant warnings and eliminate false positives (Section~\ref{sec:filters}).

@@

We randomly chose subjects belonging to various categories from subjects satisfying
the above criteria. The subjects used in our experiment are shown in Table~\ref{table:subjects},
which include end-user applications, programming tools, and games.

@@

\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox} implements a client that allows users
to drag and drop files, which are then uploaded to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions efficiently using mutlithreading execution.

@@

We ran our tool on each subject with three call graph construction
algorithms: RTA~\cite{rta}, 0-CFA, and 1-CFA~\cite{kcfa}.  When running
each call graph construction algorithm on three Android applications, we
used two configurations: with and without the reflection-aware algorithm 
(Section~\ref{sec:cg}).  We did not use more expensive algorithms like $k$-CFA ($k >$ 1),
because they can not scale to our subject programs.

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.35\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & \multicolumn{2}{|c|}{The Approach in}  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c|}{RTA }& \multicolumn{3}{|c|}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & \multicolumn{2}{|c|}{Section~\ref{sec:straightforward}}  \\
\cline{2-12}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning & \#Bug\\
\hline \hline
\multicolumn{12}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP&  12401 &  2 &  2 & 10858 & 2 & 2 & 43598 & 2 & 2& 149 & 2 \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693 & 1 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202 & 1 \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 & 1 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210 & 1 \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356 & 2 \\
 \hline
 \hline
\multicolumn{12}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 & 1 \\
 \hline
 Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 & 1 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 & 1 \\
\hline
\hline
 Total & 178279 / 178842 &  188 / 251 & 6 / 6 & 129744 / 133357 & 137 / 137& 7 / 7 & 461423 / 536358& 21 / 21 & 10 / 11 & 3521 & 11 \\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding invalid thread access errors
in multithreaded GUI programs. Column ``CG Size'' shows the
call graph size in terms of node number. Column ``\#Warning''
shows the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Columns ``RTA '', ``0-CFA'',
and ``1-CFA'' show the results of using different
call graph construction algorithms. In each cell of the table
for Android applications, a slash ``/'' separates the result of
using normal call graph construction algorithm and the reflection-aware
call graph construction algorithm. The 6 errors found in VirgoFTP, FileBunker,
S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
results of a straightforward approach (Section~\ref{sec:straightforward}) are shown at the far right.} }
\end{table*}

@@

Table~\ref{table:results} tabulates the results of running our
tool with three different call graph construction algorithms
on the subject programs. From these results, we can see our
tool found real errors from each subject on  four
supported GUI frameworks. The results vary slightly according
to the call graph algorithm used. In general, using
the 1-CFA algorithm found most errors (11 in total) and least
false positive warnings (10 in total). A comparison of using other call graph
construction algorithms will be explained in Section~\ref{sec:reflectionaware}.

We further examined the detailed results for each subject.
Among the 21 warnings issued by using the 1-CFA algorithm, 11
warnings reveals 11 distinct errors (6 are previously-unknown),
2 warnings are false positive, and the remaining 8 warnings
are redundant.

@@

As briefly mentioned in Section~\ref{sec:finding}, one way to prevent
invalid thread access errors is to wrap every GUI accessing operation
with message passing (i.e., via the safe UI methods). Thus, a
straightforward way to detect potential invalid error
is to check every method in the user code to determine whether all GUI-accessing operation
is probably wrapped. If not, this approach issues a warning.% for every violation. 
%If not, this approach issues warnings.

We implemented this straightforward approach and experimentally compared it
with our technique.% presented in Section~\ref{sec:technique}.
The far right column in Table~\ref{table:results} shows the results.
The results show that this straightforward approach could identify every
error that our technique found, but issue a huge number of warnings.
The primary reason is that this simple approach
does not globally reason about calling relationship between
threads, UI-accessing methods, and safe UI methods, thus it often incorrectly
classifies GUI accessing operations which will never be executed
in a non-UI thread as erroneous. Furthermore, our technique
outputs a method call chain with each reported error, which can help
developers understand how an invalid thread access error is triggered.

@@

We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors with less false positive warnings than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph, and may
mix the same method calls by different callers into a single node, thus
introduce imprecision.

@@

For other two Android applications (Fennec and SGTPuzzler), the errors
can be found by using a standard call graph construction algorithm. This
is because the error-related GUI objects are created explicitly, so that
the standard call graph construction algorithm is sufficient.

@@

The first variant uses DFS for graph traverse by changing
line 7 in Figure~\ref{fig:androiderror} to:
$\mathit{fringe}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
and changing queue operations (\CodeIn{enqueueAll}, \CodeIn{dequeue}, and \CodeIn{enqueue} on lines 9,
11, and 23 in Figure~\ref{fig:androiderror}, respectively)
to the corresponding statck operations (\CodeIn{pushAll}, \CodeIn{pop} and \CodeIn{push}).

As a result, this variant found 8 errors in total and missed 1 error in the FileBunker subject.
The reason is that DFS tends to search deeper into the graph, and the path it returns
may not be the shortest one and are more likely to be an infeasible path in practice.
For the FileBunker subject, paths
returned by DFS are much longer than BFS, and do not actually exist.

@@

The second variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI object without using safe UI methods. As
a result, this variant run out of memory on all subjects. We checked
the output paths before the algorithm terminated, and found none of the explored
path revealed a real error. This is because the number of
non-cyclic paths in a graph is exponentially large to the graph node number.
For a realistic call graph which often contains thousands of nodes,
it is impossible to enumerate all paths in practice.

@@

Table~\ref{table:filters} tabulates the results.
Our static analysis output thousands of warnings for the evaluated
subjects, but the proposed heuristic filters effectively reduced
the number of likely invalid warnings. On average, five heuristic
filters removed 99.96\% of the reported warnings as false positives
or redundant warnings. Specifically, heuristic filters 1 and 2 identified
29.38\% of the warnings as likely false positives, and filters 3, 4,
and 5 identified 70.58\% of the warnings as redundant warnings.
Remarkably, the 3rd heuristic filter for removing lexically redundant
reports is the most effective one on the evaluated subjects: it removes 37019 redundant warnings.

@@

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.46\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 Subject & Before & \#W & \#W & \#W & \#W& \#W \\
 Program & Filtering & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP &  21 &  21 &  3 & 3 &  2 & 2\\
 \hline
 FileBunker &  4494 &  3210 &  3210 &  642 &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1621 &  1487 &  1487 & 1487 &  6 & 6\\
 \hline
 HundsonEclipse&  3192 &  2417 &  2417 & 9 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  31978 & 9 &  1 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 2 &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  122 &  122 & 84 & 84 &  9 & 3\\
 \hline
 MyTracks &  1176 &  1176 &  441 & 441 &  63 & 1 \\
\hline
 \hline
 Total &  56214 &  40470 &  39697 &  2678 &  89 & 21 \\
 \hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
heuristic filters. Column ``Before Filtering''
shows the output warning number by the reflection-aware 1-CFA algorithm.
Results of using other algorithms show similar patterns, which are omitted for brevity.
Column ``\#W $F_{i,...,j}$'' represents the number of remaining warnings after applying
the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
Numbers in last column are taken from the subcolumn ``\#Warnings"
under column ``1-CFA'' in Table~\ref{table:results}.
} }
\end{table}

### 2012-02-03 GUIErrorDetector/paper/implementation.tex
changes based on new comments

We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
Our prototype tool takes Java bytecode as inputs, works in a fully
automatic and push-button way to detect potential invalid thread access
errors, and scales to realistic programs.  
Optionally, users may specify additional heuristics to guide call graph
traverse, and annotate call relationships for native methods (Section~\ref{sec:heuristic}).

Our current implementation supports four widely-used GUI frameworks, namely
SWT, Eclipse plugin development, Java Swing, and Android.
Our implementation %handles all of the Java language, and
also takes
all dependent libraries (e.g., \CodeIn{rt.jar} and \CodeIn{android.jar})
into analysis. We implemented the reflection-aware call graph construction
 algorithm (Section~\ref{sec:cg})
using WALA's \textit{bypass logic}. Our tool parses the configuration file
in an Android application and modifies the bytecode to replace all
reflection calls with object creation instructions.
Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our tool first uses
android-apktool~\cite{apktool} to
decrypt the apk file, and then uses the 
ded translator~\cite{Enck:2011:SAA:2028067.2028088} to convert
Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholder for the sake of efficiency. We manually re-compiled the whole
\CodeIn{android.jar} from its source code by replacing all ``stub'' classes
with real class files.

>>>>

We implemented the proposed technique using the WALA framework~\cite{walatutorial}.
Our prototype tool takes Java bytecode as input, works in a fully
automatic and push-button way to detect potential invalid thread access
errors, and scales to realistic programs.

%Optionally, users may specify additional heuristic filters (Section~\ref{sec:heuristic}) %to guide call graph traverse
%, and annotate call relationships for native methods (Section~\ref{sec:annotation}).

Our current implementation supports four widely-used GUI frameworks, namely
SWT, Eclipse plugin development, Swing, and Android.
%, including dependent libraries such as \CodeIn{rt.jar} and \CodeIn{android.jar}.
%into analysis. 
We implemented the reflection-aware call graph construction
 algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
Unlike similar tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
does not require a separated
pass of program instrumentation; instead, it
parses the configuration file in an Android application,
and then intercepts the call graph construction
process on-the-fly to replace all reflection calls with object creation statements.
Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our tool first uses
android-apktool~\cite{apktool} to
decrypt the apk file, and then uses the 
ded translator~\cite{Enck:2011:SAA:2028067.2028088} to convert
Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholders for the sake of efficiency. We manually re-compiled the whole
\CodeIn{android.jar} from its source code and replaced all ``stub'' classes
with real class files.
